### 2019-01-10 Thesis/thesis.tex
Correction.

  $\G$ is enriched in algebraic cpos, so $\alpha$ is the least upper bound of its compact approximants.  
  It follows that there is some compact $\alpha'\subset \alpha$ such that
  \begin{mathpar}
    \deno M;(\bC \to \alpha');\mu;\eta;\new_\bC;t_n \ne \bot
    \and
    \deno N;(\bC \to \alpha');\mu;\eta;\new_\bC;t_n = \bot\,.
  \end{mathpar}
  In other words:
  \begin{mathpar}
    \tit(\deno M;(\bC \to \alpha');\mu) = n\,;
    \and
    \tit(\deno M;(\bC \to \alpha');\mu) \ne n\,.
  \end{mathpar}
  Now the compact definability result for Idealized Algol \cite[17]{SamsonGuyIAActive} tells us that $\alpha'$ must be the denotation of some IA term $x\from T \ts C[x] \from \com \to \com$, which is therefore the denotation of $C[\sleep] \from \com \to \com$ in $\Kl_{R_\bC}$.
  So we get
  \begin{mathpar}
    \tit(\deno{C[\sleep] M}) = n\,;
    \and
    \tit(\deno{C[\sleep] N}) \ne n\,.
  \end{mathpar}
  By Theorem \ref{IaSleepComputationalAdequacy}, $C[\sleep] M\converges_n$ and $C[\sleep] N\not\converges_n$.  
  Therefore, $M$ and $N$ are observationally inequivalent in IA+$\sleep$.
\end{proof}

>>>>

  $\G$ is enriched in algebraic cpos, so $\alpha$ is the least upper bound of its compact approximants.  
  It follows that there is some compact $\alpha'\subset \alpha$ such that
  \begin{mathpar}
    \deno M;(\bC \to \alpha');\mu;\eta;\new_\bC;t_n \ne \bot
    \and
    \deno N;(\bC \to \alpha');\mu;\eta;\new_\bC;t_n = \bot\,.
  \end{mathpar}
  In other words:
  \begin{mathpar}
    \tit(\deno M;(\bC \to \alpha');\mu) = n\,;
    \and
    \tit(\deno N;(\bC \to \alpha');\mu) \ne n\,.
  \end{mathpar}
  Now the compact definability result for Idealized Algol \cite[17]{SamsonGuyIAActive} tells us that $\alpha'$ must be the denotation of some IA term $x\from T \ts C[x] \from \com \to \com$, which is therefore the denotation of $x\from T \ts C[x]\,\sleep \from \com$ in $\Kl_{R_\bC}$.
  So we get
  \begin{mathpar}
    \tit(\deno{C[M]\,\sleep}) = n\,;
    \and
    \tit(\deno{C[N]\,\sleep}) \ne n\,.
  \end{mathpar}
  By Theorem \ref{IaSleepComputationalAdequacy}, $C[M]\,\sleep\converges_n$ and $C[N]\,\sleep\not\converges_n$.  
  Therefore, $M$ and $N$ are observationally inequivalent in IA+$\sleep$.
\end{proof}
